Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2014-07-24 draft.tex
Add sketch of decay topology for section III.A
[notation, appendix] Check and comment on appendices C-E, change symbol of differential

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}
\usepackage{hepparticles}
\usepackage{hepnicenames}
\usepackage{hepunits}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{epstopdf}
%% Shortcuts %%
\newcommand{\dd}{\text{d}\!}
\newcommand{\refapp}[1]{app.~(\ref{app:#1})}
\newcommand{\refeq}[1]{eq.~(\ref{eq:#1})}
\newcommand{\refsec}[1]{sec.~(\ref{sec:#1})}
\newcommand{\reftab}[1]{tab.~(\ref{tab:#1})}
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\nuvec}{\vec{\nu}}
\newcommand{\thvec}{\vec{\vartheta}}
\let\oldtheta\theta
\renewcommand{\theta}{\vartheta}
%\newcommand{\GeV}{\text{GeV}}
\newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}
\let\eps\varepsilon
\newcommand{\aver}[1]{\langle #1 \rangle}
\newcommand{\est}[1]{\widehat{#1}}
\newcommand{\wwhat}[1]{\widehat{\widehat{#1}}}
\DeclareMathOperator{\cov}{Cov}
%\DeclareMathOperator{\skew}{Skew}
\DeclareMathOperator{\kurt}{Kurt}

@@

We continue with basic definitions that pertain to angular observables, and our
results in the subsequent sections. Let $\thvec = (\theta_1, \dots \theta_N)$ denote the set of all
angles, and let $\nuvec = (\nu_1, \dots \nu_M)$ denote the set of all
other non-angular kinematic variables needed to fully specify the
final state of the process under study. For example, $\nuvec$ may
include invariant masses or center-of-mass energies. We define an
angular observable $S_i$ as a coefficient in the probability density
function (PDF) of the process by means of
\begin{align}
    \label{eq:def-P}
    P(\nuvec, \thvec) \equiv \sum_i S_i(\nuvec) \times f_i(\thvec)\,.
\end{align}
Here, the dependence on the $n$ decay angles $\thvec$ has been
explicitly factored out in terms of the angular functions
$f_i(\thvec)$, which we assume to fulfill the orthonormality relations
\begin{equation}
    \label{eq:def-ortho-rel}
    \int_\Omega f_i(\thvec) f_j(\thvec) \dd^N \theta = \delta_{ij}\,,
\end{equation}
with $\Omega$ representing the full angular phase space relevant to the process.
For the purpose of this letter, however, it suffices that the system
of angular functions $f_i(\thvec)$ can be transformed into an
orthonormal basis. The transformation needs to be worked out on a
case-by-case basis. For a selection of $B$ decays which we consider the most interesting
we list the transformations in a series of appendices \ref{app:btokll} through
\ref{app:lambdabtolambdall}.\\

For particle decays, $P$ is generally expressed in terms of the fully differential decay width,
\begin{align}
    \label{eq:def-P-decay}
    P(\nuvec, \thvec) \equiv \frac{1}{\Gamma}\frac{\dd^{N+M}\Gamma}{\dd \nu_1 \dots \dd \nu_M\, \dd \theta_1 \dots \theta_N}\,,
\end{align}
where $\Gamma$ is the total decay width. For a scattering process, one can similarly use
\begin{align}
    \label{eq:def-P-scattering}
    P(\nuvec, \thvec) \equiv \frac{1}{\sigma}\frac{\dd^{N+M}\sigma}{\dd \nu_1 \dots \dd \nu_M\, \dd \theta_1 \dots \theta_N}\,,
\end{align}
where the total cross section $\sigma$ is used for the
normalization. Since the determination of the total decay width or
total cross section can be quite difficult, we emphasize that
different normalizations for $P$ can be used.  For instance, the total
decay width (or cross section) of the process of interest can be
replaced by the corresponding quantity of a control-channel
process. This change of normalization is equivalent to a linear rescaling of
the angular observables $\lbrace S_i\rbrace$; thus ratios or similar suitable combinations
of the angular observables are invariant.\\

@@

The orthonormality relations \refeq{def-ortho-rel} imply that a single angular observable $S_i$
can be projected out of the full PDF $P$ by means of
\begin{equation}
    \label{eq:det-Pi-analytical}
    S_i(\nuvec) = \int_{\Omega} \hat{f}_i(\thvec) P(\nuvec, \thvec) \dd^N \theta\,.
\end{equation}
where $\lbrace \hat{f}_i \rbrace$ denotes a \emph{dual basis} of angular function. In all generality
the bases $\lbrace f_i \rbrace$ and $\lbrace \hat{f}_i \rbrace$ are not identical. This is the
case for our selection of applications in appendices \ref{app:btokll} through \ref{app:lambdabtolambdall}.\\

It is sensible to refer to the angular observable $S_i$ as the \emph{$\hat{f}_i$-moment} of the PDF $P$.
We emphasize that a relation of type \refeq{det-Pi-analytical} holds for any combination of
scalar product and orthonormal basis of angular functions $\lbrace f_i \rbrace$; \ie, there is no unique
basis of angular functions. For the proof we refer to ref. \cite{Dighe:1998vk}.\\
In addition, integration over the non-angular variables yields
\begin{equation}
    \langle S_i\rangle
    \equiv \int S_i(\nuvec) \dd^M \nu
    = \int \left[\int_{\Omega} \hat{f}_i(\thvec) P(\nuvec,\thvec) \dd^N\theta\right]\dd^M \nu\,.
\end{equation}
The remainder of this section describes the method of moments, in which we replace the
analytical integration \refeq{det-Pi-analytical} by Monte Carlo (MC) estimators.\\

The central tenet of MC integration is the fact that the expectation value $E_P[g]$ of some function
$g(x)$ under the probability density $P(x)$,
\begin{equation}
    E_P[g] \equiv \int g(x) P(x) \dd x
\end{equation}
can be approximated \cite{MCSM-2004} by an MC estimator $\est{E_P[g]}$
\begin{equation}
    \label{eq:mc-id}
    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{K} \sum_{k=1} g(x^{(k)})
\end{equation}
due to the strong law of large numbers for $K \to \infty$ assuming
that the variates $x^{(k)}$, $k = 1, \dots, K$ are distributed as
$P$; i.e.,
\begin{equation}
    x^{(k)} \sim P\,.
\end{equation}
Throughout this letter we denote all MC estimators with a wide hat.\\

Application of \refeq{mc-id} then yields
\begin{equation}
    \langle S_i\rangle \to \widehat{\langle S_i\rangle} = \frac{1}{K} \sum_{k=1}^{K} \hat{f}_i(x^{(k)})\,.
\end{equation}
It is often of interest to obtain the $\nuvec$- observables integrated
over certain ranges of $\nuvec$; i.e., binned measurements of $\langle
S_i\rangle$.
Therefore, we introduce the bin-integrated quantity
\begin{align}
    \langle S_i\rangle_{\vec{a},\vec{b}}
    & = \int_{\vec{a}}^{\vec{b}} S_i(\nuvec) \dd^M \nu\\
    & = \int_{\vec{a}}^{\vec{b}} \left[\int_{\Omega} \hat{f}_i(\thvec) P(\nuvec,\thvec) \dd^N\theta\right]\dd^M \nu\\
    & = \int \left[\int_{\Omega} \hat{f}_i(\thvec) P(\nuvec,\thvec)
        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,
        \dd^N\theta\right]\dd^M \nu\,,
\end{align}
where the argument of the indicator function $ \mathbf{1}(\vec{a} \le
\nuvec \le \vec{b})$ is to be interpreted componentwise.
Application of \refeq{mc-id} immediately yields
\begin{equation}
    \label{eq:bin-importance}
    \widehat{\langle S_i\rangle_{\vec{a},\vec{b}}}
    = \frac{1}{K} \sum_{k=1}^{K} \hat{f}_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
\end{equation}
This basically reduces the estimation of
$\aver{S_i}_{\vec{a},\vec{b}}$ to a (weighted) counting experiment. In
the limit $N \to \infty$, the random vector $( \dots,
\aver{S_i}_{\vec{a},\vec{b}}, \dots)$ follows a multivariate Gaussian
distribution \citeneeded\fred{Robert,Casella?}
with the mean vector estimated by \refeq{bin-importance}, and the covariance
estimated as
\begin{equation}
    \cov[\aver{S_i},\aver{S_j}]_{\vec{a},\vec{b}} \to \est{\cov}[\aver{S}_i, \aver{S}_j]_{\vec{a},\vec{b}}
        = \frac{1}{K - 1} \sum_{k=1}^{K} \big[\hat{f}_i(x^{(k)}) - \est{\langle S_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[\hat{f}_j(x^{(k)}) - \widehat{\langle S_j\rangle_{\vec{a},\vec{b}}}\big]
        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
\end{equation}
We would like to emphasize that the sample covariance should rapidly converge towards the true covariance matrix.
We propose to declare convergence once estimators for skewness and kurtosis are sufficiently small,
\begin{equation}
    \est{\operatorname{Skew}}[\aver{S_i},\aver{S_j}] \ll 1\,\,\text{ and }\,\,\est{\kurt}[\aver{S_i},\aver{S_j}] \ll 1\,.
\end{equation}

@@

\fred{Paragraph is very specific to one physics case. Needs a drawing}

@@

The PDF for the decay $\bar{B}\to\bar{K}\ell^+\ell^-$ has been calculated for the most
complete basis of dimension-six $b\to s \ell^+\ell^-$ operators. It reads \cite{Bobeth:2007dw,Bobeth:2012vn}
\begin{equation}
    P(q^2, \cos\theta_1) = \frac{1}{\Gamma} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1} = \frac{a(q^2)}{\Gamma} + \frac{b(q^2)}{\Gamma} \cos\theta_1 + \frac{c(q^2)}{\Gamma} \cos^2\theta_1 = \sum_i P_i f_i(\cos\theta_1)\,,
\end{equation}
where the basis of angular functions $\lbrace f_i\rbrace$ reads
\begin{equation}
\begin{aligned}
    f_1 & = 1\,, &
    f_2 & = \cos\theta_1\,, &
    f_2 & = \cos^2\theta_1\,.
\end{aligned}
\end{equation}
Here we denote the dilepton mass squared as $q^2$, and the dilepton helicity angle as $\theta_1 \equiv \theta_{\ell}$. We transform the PDF from a $\cos\theta_1$-dependence
to a $\theta_1$-dependence,
\begin{equation}
    P(q^2, \theta_1) = \sum_i P_i f_i(\cos\theta_1) \sin \theta_1\,.
\end{equation}
where we define $P_{\lbrace 1,2,3\rbrace} \equiv \lbrace a, b, c\rbrace / \Gamma$.\\

The dual basis $\lbrace \hat{f}_i\rbrace$ reads
\begin{equation}
\begin{aligned}
    \hat{f}_1 & = \frac{9}{8} - \frac{15}{8}\cos^2\theta_1\,, &
    \hat{f}_2 & = \frac{3}{2}\cos\theta_1\,, &
    \hat{f}_3 & = -\frac{15}{8} + \frac{45}{8}\cos^2\theta_1\,,
\end{aligned}
\end{equation}
such that
\begin{equation}
    \int_0^\pi \dd \theta_1\hat{f}_i(\theta_1) P(q^2, \theta_1) = S_i(q^2)\,.
\end{equation}

@@

The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ -- up to and including P-wave contributions -- has been calculated
for the most general basis of dimension-six $b\to s$ operators. It reads, expressed in terms of the angular observables $\lbrace J_i\rbrace$ \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\dd\Gamma/\dd q^2} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1\,\dd \cos\theta_2\,\dd \theta_3} = \frac{3}{8\pi} \sum_k \frac{J_{k}(q^2)}{\dd\Gamma/\dd q^2} f_k(\cos\theta_1, \cos\theta_2, \theta_3)\,,
\end{equation}
where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K}$ is the $\bar{K}\pi$ helicity angle, and $\theta_3 \equiv \phi$ is the azimuthal angle.
The $q^2$-differential decay width reads
\begin{equation}
    \frac{\dd\Gamma}{\dd q^2} = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
\end{equation}
The angular functions\footnote{%
    We consistently use the label "$i$" to denote angular function and observables that arise
    from interference between S-wave and P-wave amplitudes. Our convention is related to the convention
    of \cite{Bobeth:2012vn} through $f_{1i} \leftrightarrow f_{1sc}$, $f_{2i} \leftrightarrow f_{2sc}$.
} read \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
\begin{aligned}
    f_{1s} & = \sin^2\theta_2 &
    f_{1c} & = \cos^2\theta_2 &
    f_{1i} & = \cos\theta_2\\
    f_{2s} & = \sin^2\theta_2 \cos 2\theta_1 &
    f_{2c} & = \cos^2\theta_2 \cos 2\theta_1 &
    f_{2i} & = \cos\theta_2 \cos 2\theta_1\\
    f_{3}  & = \sin^2\theta_2\sin^2\theta_1 \cos 2\theta_3 &
    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\theta_3\\
    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\theta_3 & & &
    f_{4i} & = \sin\theta_2 \sin 2\theta_1 \cos\theta_3\\
    f_{5}  & = \sin 2\theta_2 \sin \theta_1 \cos\theta_3 & & &
    f_{5i} & = \sin\theta_2 \sin \theta_1 \cos\theta_3\\
    f_{6s} & = \sin^2\theta_2 \cos\theta_1 &
    f_{6c} & = \cos^2\theta_2 \cos\theta_1\\
    f_{7}  & = \sin 2\theta_2 \sin \theta_1 \sin\theta_3 & & &
    f_{7i} & = \sin\theta_2 \sin \theta_1 \sin\theta_3\\
    f_{8}  & = \sin 2\theta_2 \sin 2\theta_1 \sin\theta_3 & & &
    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\theta_3\,.
\end{aligned}
\end{equation}
We indicate contributions from the interference of S waves and P waves by an index \emph{i}. In terms of the angles $\theta_1$ and $\theta_2$, instead of their cosines, the PDF reads
\begin{equation}
    P(q^2, \theta_1, \theta_2, \theta_3) = \frac{3}{8\pi} \sum_k S_k(q^2) f_k(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
\end{equation}
where we also define $S_k(q^2) \equiv J_k(q^2) / (\dd\Gamma/\dd q^2)$.\\

>>>>

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}
\usepackage{hepparticles}
\usepackage{hepnicenames}
\usepackage{hepunits}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{epstopdf}
%% Shortcuts %%
\newcommand{\rmdx}[1]{\mbox{d} #1 \,} % differential
\newcommand{\refapp}[1]{app.~(\ref{app:#1})}
\newcommand{\refeq}[1]{eq.~(\ref{eq:#1})}
\newcommand{\refsec}[1]{sec.~(\ref{sec:#1})}
\newcommand{\reftab}[1]{tab.~(\ref{tab:#1})}
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\nuvec}{\vec{\nu}}
\newcommand{\thvec}{\vec{\vartheta}}
\let\oldtheta\theta
\renewcommand{\theta}{\vartheta}
%\newcommand{\GeV}{\text{GeV}}
\newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}
\let\eps\varepsilon
\newcommand{\aver}[1]{\langle #1 \rangle}
\newcommand{\est}[1]{\widehat{#1}}
\newcommand{\wwhat}[1]{\widehat{\widehat{#1}}}
\DeclareMathOperator{\cov}{Cov}
%\DeclareMathOperator{\skew}{Skew}
\DeclareMathOperator{\kurt}{Kurt}

@@

We continue with basic definitions that pertain to angular observables, and our
results in the subsequent sections. Let $\thvec = (\theta_1, \dots \theta_N)$ denote the set of all
angles, and let $\nuvec = (\nu_1, \dots \nu_M)$ denote the set of all
other non-angular kinematic variables needed to fully specify the
final state of the process under study. For example, $\nuvec$ may
include invariant masses or center-of-mass energies. We define an
angular observable $S_i$ as a coefficient in the probability density
function (PDF) of the process by means of
\begin{align}
    \label{eq:def-P}
    P(\nuvec, \thvec) \equiv \sum_i S_i(\nuvec) \times f_i(\thvec)\,.
\end{align}
Here, the dependence on the $n$ decay angles $\thvec$ has been
explicitly factored out in terms of the angular functions
$f_i(\thvec)$, which we assume to fulfill the orthonormality relations
\begin{equation}
    \label{eq:def-ortho-rel}
    \int_\Omega \rmdx{^N \theta} f_i(\thvec) f_j(\thvec)  = \delta_{ij}\,,
\end{equation}
with $\Omega$ representing the full angular phase space relevant to the process.
For the purpose of this letter, however, it suffices that the system
of angular functions $f_i(\thvec)$ can be transformed into an
orthonormal basis. The transformation needs to be worked out on a
case-by-case basis. For a selection of $B$ decays which we consider the most interesting
we list the transformations in a series of appendices \ref{app:btokll} through
\ref{app:lambdabtolambdall}.\\

For particle decays, $P$ is generally expressed in terms of the fully differential decay width,
\begin{align}
    \label{eq:def-P-decay}
    P(\nuvec, \thvec) \equiv \frac{1}{\Gamma}\frac{\rmdx{^{N+M}\Gamma}}{\rmdx{\nu_1} \dots \rmdx{\nu_M} \rmdx{\theta_1} \dots \rmdx{\theta_N}}\,,
\end{align}
where $\Gamma$ is the total decay width. For a scattering process, one can similarly use
\begin{align}
    \label{eq:def-P-scattering}
    P(\nuvec, \thvec) \equiv \frac{1}{\sigma}\frac{\rmdx{^{N+M}\sigma}}{\rmdx{\nu_1} \dots \rmdx{\nu_M} \rmdx{\theta_1} \dots \rmdx{\theta_N}}\,,
\end{align}
where the total cross section $\sigma$ is used for the
normalization. Since the determination of the total decay width or
total cross section can be quite difficult, we emphasize that
different normalizations for $P$ can be used.  For instance, the total
decay width (or cross section) of the process of interest can be
replaced by the corresponding quantity of a control-channel
process. This change of normalization is equivalent to a linear rescaling of
the angular observables $\lbrace S_i\rbrace$; thus ratios or similar suitable combinations
of the angular observables are invariant.\\

@@

The orthonormality relations \refeq{def-ortho-rel} imply that a single angular observable $S_i$
can be projected out of the full PDF $P$ by means of
\begin{equation}
    \label{eq:det-Pi-analytical}
    S_i(\nuvec) = \int_{\Omega} \rmdx{^N \theta} \hat{f}_i(\thvec) P(\nuvec, \thvec)\,.
\end{equation}
where $\lbrace \hat{f}_i \rbrace$ denotes a \emph{dual basis} of angular function. In all generality
the bases $\lbrace f_i \rbrace$ and $\lbrace \hat{f}_i \rbrace$ are not identical. This is the
case for our selection of applications in appendices \ref{app:btokll} through \ref{app:lambdabtolambdall}.\\

It is sensible to refer to the angular observable $S_i$ as the \emph{$\hat{f}_i$-moment} of the PDF $P$.
We emphasize that a relation of type \refeq{det-Pi-analytical} holds for any combination of
scalar product and orthonormal basis of angular functions $\lbrace f_i \rbrace$; \ie, there is no unique
basis of angular functions. For the proof we refer to ref. \cite{Dighe:1998vk}.\\
In addition, integration over the non-angular variables yields
\begin{equation}
    \langle S_i\rangle
    \equiv \int \rmdx{^M \nu} S_i(\nuvec)
    = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N \theta}\hat{f}_i(\thvec) P(\nuvec,\thvec) \right].
\end{equation}
The remainder of this section describes the method of moments, in which we replace the
analytical integration \refeq{det-Pi-analytical} by Monte Carlo (MC) estimators.\\

The central tenet of MC integration is the fact that the expectation value $E_P[g]$ of some function
$g(x)$ under the probability density $P(x)$,
\begin{equation}
    E_P[g] \equiv \int \rmdx{x} g(x) P(x)
\end{equation}
can be approximated \cite{MCSM-2004} by an MC estimator $\est{E_P[g]}$
\begin{equation}
    \label{eq:mc-id}
    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{K} \sum_{k=1} g(x^{(k)})
\end{equation}
due to the strong law of large numbers for $K \to \infty$ assuming
that the variates $x^{(k)}$, $k = 1, \dots, K$ are distributed as
$P$; i.e.,
\begin{equation}
    x^{(k)} \sim P\,.
\end{equation}
Throughout this letter we denote all MC estimators with a wide hat.\\

Application of \refeq{mc-id} then yields
\begin{equation}
    \langle S_i\rangle \to \widehat{\langle S_i\rangle} = \frac{1}{K} \sum_{k=1}^{K} \hat{f}_i(x^{(k)})\,.
\end{equation}
It is often of interest to obtain the $\nuvec$- observables integrated
over certain ranges of $\nuvec$; i.e., binned measurements of $\langle
S_i\rangle$.
Therefore, we introduce the bin-integrated quantity
\begin{align}
    \langle S_i\rangle_{\vec{a},\vec{b}}
    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} S_i(\nuvec)\\
    & = \int_{\vec{a}}^{\vec{b}} \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} \hat{f}_i(\thvec) P(\nuvec,\thvec)  \right]\\
    & = \int \rmdx{^M \nu} \left[\int_{\Omega} \rmdx{^N\theta} \hat{f}_i(\thvec) P(\nuvec,\thvec)
        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,
        \right],
\end{align}
where the argument of the indicator function $ \mathbf{1}(\vec{a} \le
\nuvec \le \vec{b})$ is to be interpreted componentwise.
Application of \refeq{mc-id} immediately yields
\begin{equation}
    \label{eq:bin-importance}
    \widehat{\langle S_i\rangle_{\vec{a},\vec{b}}}
    = \frac{1}{K} \sum_{k=1}^{K} \hat{f}_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
\end{equation}
This basically reduces the estimation of
$\aver{S_i}_{\vec{a},\vec{b}}$ to a (weighted) counting experiment. In
the limit $N \to \infty$, the random vector $( \dots,
\aver{S_i}_{\vec{a},\vec{b}}, \dots)$ follows a multivariate Gaussian
distribution \citeneeded\fred{Robert,Casella?}
with the mean vector estimated by \refeq{bin-importance}, and the covariance
estimated as
\begin{equation}
    \cov[\aver{S_i},\aver{S_j}]_{\vec{a},\vec{b}} \to \est{\cov}[\aver{S}_i, \aver{S}_j]_{\vec{a},\vec{b}}
        = \frac{1}{K - 1} \sum_{k=1}^{K} \big[\hat{f}_i(x^{(k)}) - \est{\langle S_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[\hat{f}_j(x^{(k)}) - \widehat{\langle S_j\rangle_{\vec{a},\vec{b}}}\big]
        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
\end{equation}
We would like to emphasize that the sample covariance should rapidly converge towards the true covariance matrix.
We propose to declare convergence once estimators for skewness and kurtosis are sufficiently small,
\begin{equation}
    \est{\operatorname{Skew}}[\aver{S_i},\aver{S_j}] \ll 1\,\,\text{ and }\,\,\est{\kurt}[\aver{S_i},\aver{S_j}] \ll 1\,.
\end{equation}

@@

\begin{figure}
    \includegraphics[width=.6\textwidth]{fig-topology.pdf}
    \caption{Decay topology for decays $B\to P_1 P_2 \ell_1 \bar\ell_2$. \label{fig:topology}}
\end{figure}

@@

The PDF for the decay $\bar{B}\to\bar{K}\ell^+\ell^-$ has been calculated for the most
complete basis of dimension-six $b\to s \ell^+\ell^-$ operators. It reads \cite{Bobeth:2007dw,Bobeth:2012vn}
\begin{equation}
    P(q^2, \cos\theta_1) = \frac{1}{\Gamma} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1}} = \frac{a(q^2)}{\Gamma} + \frac{b(q^2)}{\Gamma} \cos\theta_1 + \frac{c(q^2)}{\Gamma} \cos^2\theta_1 = \sum_i P_i f_i(\cos\theta_1)\,,
\end{equation}
where the basis of angular functions $\lbrace f_i\rbrace$ reads
\begin{equation}
\begin{aligned}
    f_1 & = 1\,, &
    f_2 & = \cos\theta_1\,, &
    f_2 & = \cos^2\theta_1\,.
\end{aligned}
\end{equation}
Here we denote the dilepton mass squared as $q^2$, and the dilepton helicity angle as $\theta_1 \equiv \theta_{\ell}$. We transform the PDF from a $\cos\theta_1$-dependence
to a $\theta_1$-dependence,
\begin{equation}
    P(q^2, \theta_1) = \sum_i P_i f_i(\cos\theta_1) \sin \theta_1\,.
\end{equation}
where we define $P_{\lbrace 1,2,3\rbrace} \equiv \lbrace a, b, c\rbrace / \Gamma$.\\

The dual basis $\lbrace \hat{f}_i\rbrace$ reads
\begin{equation}
\begin{aligned}
    \hat{f}_1 & = \frac{9}{8} - \frac{15}{8}\cos^2\theta_1\,, &
    \hat{f}_2 & = \frac{3}{2}\cos\theta_1\,, &
    \hat{f}_3 & = -\frac{15}{8} + \frac{45}{8}\cos^2\theta_1\,,
\end{aligned}
\end{equation}
such that
\begin{equation}
    \int_0^\pi \rmdx{\theta_1} \hat{f}_i(\theta_1) P(q^2, \theta_1) = S_i(q^2)\,.
\end{equation}

@@

The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ --- up to and including P-wave contributions --- has been calculated
for the most general basis of dimension-six $b\to s$ operators. It reads, expressed in terms of the angular observables $\lbrace J_i\rbrace$ \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\rmdx{\Gamma}/\rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \frac{3}{8\pi} \sum_k \frac{J_{k}(q^2)}{\rmdx{\Gamma} /\, \rmdx{q^2}} f_k(\cos\theta_1, \cos\theta_2, \theta_3)\,,
\end{equation}
where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K}$ is the $\bar{K}\pi$ helicity angle, and $\theta_3 \equiv \phi$ is the azimuthal angle.
The $q^2$-differential decay width reads
\begin{equation}
    \frac{\rmdx{\Gamma}}{\rmdx{q^2}} = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
\end{equation}
The angular functions\footnote{%
    We consistently use the label "$i$" to denote angular function and observables that arise
    from interference between S-wave and P-wave amplitudes. Our convention is related to the convention
    of \cite{Bobeth:2012vn} through $f_{1i} \leftrightarrow f_{1sc}$, $f_{2i} \leftrightarrow f_{2sc}$.
} read \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
\begin{aligned}
    f_{1s} & = \sin^2\theta_2 &
    f_{1c} & = \cos^2\theta_2 &
    f_{1i} & = \cos\theta_2\\
    f_{2s} & = \sin^2\theta_2 \cos 2\theta_1 &
    f_{2c} & = \cos^2\theta_2 \cos 2\theta_1 &
    f_{2i} & = \cos\theta_2 \cos 2\theta_1\\
    f_{3}  & = \sin^2\theta_2\sin^2\theta_1 \cos 2\theta_3 &
    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\theta_3 &
    f_{4i} & = \sin\theta_2 \sin 2\theta_1 \cos\theta_3\\
    f_{5}  & = \sin 2\theta_2 \sin \theta_1 \cos\theta_3 & & &
    f_{5i} & = \sin\theta_2 \sin \theta_1 \cos\theta_3\\
    f_{6s} & = \sin^2\theta_2 \cos\theta_1 &
    f_{6c} & = \cos^2\theta_2 \cos\theta_1\\
    f_{7}  & = \sin 2\theta_2 \sin \theta_1 \sin\theta_3 & & &
    f_{7i} & = \sin\theta_2 \sin \theta_1 \sin\theta_3\\
    f_{8}  & = \sin 2\theta_2 \sin 2\theta_1 \sin\theta_3 & & &
    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\theta_3\\
    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\theta_3\\
\end{aligned}
\end{equation}
We indicate contributions from the interference of S waves and P waves by an index \emph{i}. In terms of the angles $\theta_1$ and $\theta_2$, instead of their cosines, the PDF reads
\begin{equation}
    P(q^2, \theta_1, \theta_2, \theta_3) = \frac{3}{8\pi} \sum_k S_k(q^2) f_k(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
\end{equation}
where we also define $S_k(q^2) \equiv J_k(q^2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.\\

The dual basis reads
\begin{equation}
\begin{aligned}
    \hat{f}_{1s} & = \frac{\big( 63 \sin^2\theta_2 - 42 \cos^2\theta_2\big) + \big(  45 \sin^2\theta_2 - 30 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
    \hat{f}_{1c} & = \frac{\big(-21 \sin^2\theta_2 + 84 \cos^2\theta_2\big) + \big( -15 \sin^2\theta_2 + 60 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,\\
    \hat{f}_{2s} & = \frac{\big( 45 \sin^2\theta_2 - 30 \cos^2\theta_2\big) + \big(+135 \sin^2\theta_2 - 90 \cos^2\theta_2\big)\cos 2\theta_1}{64} \,,\\
    \hat{f}_{2c} & = \frac{\big(-15 \sin^2\theta_2 + 60 \cos^2\theta_2\big) + \big( -45 \sin^2\theta_2 +180 \cos^2\theta_2\big)\cos 2\theta_1}{32} \,,
\end{aligned}
\end{equation}
as well as
\begin{equation}
\begin{aligned}
    \hat{f}_{1i} & = \frac{\big(21 + 15 \cos1\theta_2\big)\cos\theta_2}{16}               \,,&
    \hat{f}_{2i} & = \frac{\big(15 + 45 \cos1\theta_2\big)\cos\theta_2}{16}               \,,\\
    \hat{f}_{3}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \cos2\theta_3}{32}                \,,& &\\
    \hat{f}_{4}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \cos \theta_3}{32}                \,,&
    \hat{f}_{4i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \cos \theta_3}{8}                 \,,\\
    \hat{f}_{5}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \cos \theta_3}{8}                 \,,&
    \hat{f}_{5i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \cos \theta_3}{2}                 \,,\\
    \hat{f}_{6s} & = \frac{\big( 9\sin^2\theta_2 -  6 \cos^2\theta_2\big)\cos\theta_1}{4} \,,&
    \hat{f}_{6c} & = \frac{\big(-3\sin^2\theta_2 + 12 \cos^2\theta_2\big)\cos\theta_1}{2} \,,\\
    \hat{f}_{7}  & = \frac{15 \sin 2\theta_2 \sin  \theta_1 \sin \theta_3}{8}                 \,,&
    \hat{f}_{7i} & = \frac{3  \sin  \theta_2 \sin  \theta_1 \sin \theta_3}{2}                 \,,\\
    \hat{f}_{8}  & = \frac{75 \sin 2\theta_2 \sin 2\theta_1 \sin \theta_3}{32}                \,,&
    \hat{f}_{8i} & = \frac{15 \sin  \theta_2 \sin 2\theta_1 \sin \theta_3}{8}                 \,,\\
    \hat{f}_{9}  & = \frac{75 \sin^2\theta_2 \sin^2\theta_1 \sin2\theta_3}{32}                \,.\\
\end{aligned}
\end{equation}
such that
\begin{equation}
    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\theta_3} \hat{f}_k(\theta_1,\theta_2,\theta_3) P(q^2, \theta_1,\theta_2,\theta_3) = S_k(q^2)\,.
\end{equation}
